Untitled

### 2020-08-28 paper_results.Rmd
update
clean up

  empty_re <- mixor(intake_2 ~ 1, data = meals,
                    id = ptid, link = "logit") # With random effect

  summary(empty_re)

@@

  basic_re <- mixor(intake_2 ~ day + meal, data = meals,
                 id = ptid, link = "logit") # With random effect

  summary(basic_re)

@@

  basic_re_2$alpha

@@

```
```{r}

@@

  print(summarytools::dfSummary(patients), method = "render")

@@

  print(summarytools::dfSummary(meals), method = "render")

>>>>

# empty_re <- mixor(intake_2 ~ 1, data = meals,
#                   id = ptid, link = "logit") # With random effect
# 
# summary(empty_re)

@@

# basic_re <- mixor(intake_2 ~ day + meal, data = meals,
#                id = ptid, link = "logit") # With random effect
# 
# summary(basic_re)

@@

@@

Less meal completion with "high" frailty.

@@

#  print(summarytools::dfSummary(patients), method = "render")

@@

#  print(summarytools::dfSummary(meals), method = "render")
